---
title: "SEM Parameter Conditions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SEM Parameter Conditions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

For `lavaan` simulations, `mcsimr` lets users vary population parameters across
conditions. This is useful when a Monte Carlo study asks how performance changes
as loadings, factor variances, structural paths, residual variances, or residual
covariances change.

## Define parameters to vary

Use `sem_parameter_conditions()` with lavaan's usual parameter language:

```{r, eval = FALSE}
pc <- sem_parameter_conditions(
  lhs = c("f", "f", "y1"),
  op = c("=~", "~~", "~~"),
  rhs = c("y2", "f", "y1"),
  values = list(
    c(0.60, 0.80),
    c(0.80, 1.00),
    c(0.40, 0.60)
  )
)
```

The function crosses the supplied values, so the example above creates a full
condition grid across the loading, factor variance, and residual variance.

## Build the simulation specification

```{r, eval = FALSE}
population_model <- "
f =~ 0.70*y1 + 0.80*y2 + 0.90*y3
f ~~ 1*f
y1 ~~ 0.51*y1
y2 ~~ 0.36*y2
y3 ~~ 0.19*y3
"

spec <- sem_sim_spec(
  population_model = population_model,
  fitted_model = "f =~ y1 + y2 + y3",
  n = c(100, 250, 500),
  reps = 1000,
  parameter_conditions = pc,
  seed = 20260608
)

sem_condition_grid(spec)
```

## Run with checkpoints

```{r, eval = FALSE}
study <- run_simulation_study(
  spec,
  workers = available_cores(),
  checkpoint_dir = "results/checkpoints/sem-demo",
  resume = TRUE,
  output_dir = "results/sem-demo"
)
```

The summary includes the parameter-condition label so APA-style tables and plots
can be interpreted by condition, not only by numeric condition id.
