---
title: "SEM Parameter Conditions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SEM Parameter Conditions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

For `lavaan` simulations, `mcsimr` lets users vary population parameters across
conditions. This is useful when a Monte Carlo study asks how performance changes
as loadings, factor variances, structural paths, residual variances, or residual
covariances change.

## Define parameters to vary

Use `sem_parameter_conditions()` with lavaan's usual parameter language:

```{r, eval = FALSE}
pc <- sem_parameter_conditions(
  lhs = c("f", "f", "y1"),
  op = c("=~", "~~", "~~"),
  rhs = c("y2", "f", "y1"),
  values = list(
    c(0.60, 0.80),
    c(0.80, 1.00),
    c(0.40, 0.60)
  )
)
```

The function crosses the supplied values, so the example above creates a full
condition grid across the loading, factor variance, and residual variance.

## Add missingness and nonnormality factors

`sem_sim_spec()` can also cross lavaan parameter conditions with missing-data
rates, missing-data mechanisms, and nonnormality settings. Missing values are
imposed after data generation, so use an appropriate lavaan missing-data option
such as FIML when the design includes missingness.

Supported missing-data mechanisms are:

- `none`: do not impose missing values even when crossing placeholder conditions;
- `mcar`: missing completely at random for the target variables;
- `mar`: missingness in target variables depends on a separate observed driver;
- `mnar`: missingness in each target variable depends on that variable's own value.

The preset catalog is a quick way to start from common SEM templates:

```{r, eval = FALSE}
sem_model_presets()
preset <- sem_model_preset("latent_mediation")
```

## Build the simulation specification

```{r, eval = FALSE}
preset <- sem_model_preset("latent_mediation")

spec <- sem_sim_spec(
  population_model = preset$population_model,
  fitted_model = preset$fitted_model,
  n = c(100, 250, 500),
  reps = 1000,
  parameter_conditions = preset$parameter_conditions,
  missing = "fiml",
  missing_rate = c(0, 0.10, 0.20),
  missing_mechanism = c("mcar", "mar", "mnar"),
  missing_targets = c("m1", "m2", "m3", "y1", "y2", "y3"),
  missing_driver = "x1",
  missing_slope = 1,
  skewness = c(0, 1),
  kurtosis = c(0, 2),
  seed = 20260608
)

sem_condition_grid(spec)
sem_model_parameters(preset$population_model)
sem_design_summary(spec)
sem_design_warnings(spec)
validate_simulation_design(spec)
```

## Add misspecification and groups

Misspecification presets create common fitted-model deviations while keeping the
population model explicit. Multiple-group starters simulate the same population
model in labeled groups and fit a lavaan multiple-group model.

```{r, eval = FALSE}
sem_misspecification_presets()

grouped <- sem_sim_spec(
  population_model = preset$population_model,
  fitted_model = preset$fitted_model,
  n = c(200, 400),
  reps = 500,
  parameter_conditions = preset$parameter_conditions,
  misspecification = "omit_structural_path",
  group_variable = "study_group",
  group_labels = c("reference", "comparison"),
  group_proportions = c(.60, .40),
  seed = 20260608
)

validate_simulation_design(grouped)
```

## Run with checkpoints

```{r, eval = FALSE}
study <- run_simulation_study(
  spec,
  workers = available_cores(),
  checkpoint_dir = "results/checkpoints/sem-demo",
  resume = TRUE,
  output_dir = "results/sem-demo"
)

study$run_manifest
cat(study$methods_text)
read_run_manifest("results/checkpoints/sem-demo")

retry_failed_conditions(
  spec,
  checkpoint_dir = "results/checkpoints/sem-demo",
  workers = 4
)
```

## Split large designs into shards

For HPC systems or multiple desktop sessions, split the condition grid into
deterministic shards. Each shard writes to its own checkpoint subdirectory.

```{r, eval = FALSE}
condition_shards(spec, shards = 8)

run_simulation_shard(
  spec,
  shard_id = 1,
  shards = 8,
  workers = 8,
  checkpoint_dir = "results/checkpoints/sem-shards",
  output_dir = "results/sem-shards"
)

all_raw <- collect_checkpoint_results("results/checkpoints/sem-shards")
run_failure_summary("results/checkpoints/sem-shards/shard-001-of-008")
runtime_estimate_from_manifest("results/checkpoints/sem-shards/shard-001-of-008")
```

The summary includes the parameter-condition label, missing rate, missing-data
mechanism, skewness, and kurtosis so APA-style tables and plots can be
interpreted by condition, not only by numeric condition id.
