---
title: "Monte Carlo Simulation Report"
format: html
execute:
  echo: true
  warning: false
  message: false
---

```{r}
library(mcsimr)
library(yaml)
```

## Study Design

```{r}
spec <- yaml::read_yaml("spec.yml")
if (identical(spec$type, "sem")) {
  class(spec) <- c("mcsimr_sem_spec", "mcsimr_spec", "list")
} else {
  class(spec) <- c("mcsimr_ols_spec", "mcsimr_spec", "list")
}
spec$study_name
spec$research_question
```

## Run Simulation

```{r}
source("run.R")
```

## Methods Text

```{r, results='asis'}
cat(methods_text)
```

## Model Equations

```{r, results='asis'}
if (length(equations_latex)) {
  for (eq in equations_latex) {
    cat("$$\n", eq, "\n$$\n\n", sep = "")
  }
}
```

### Raw LaTeX

```{r, results='asis'}
if (length(equations_latex)) {
  cat("```tex\n")
  cat(paste(equations_latex, collapse = "\n"))
  cat("\n```\n")
}
```

## APA-Style Performance Table

```{r}
cat(paste(apa_table$markdown, collapse = "\n"))
```

## Metric Summary

```{r}
summary
```

## Run Manifest

```{r}
if (exists("run_manifest") && nrow(run_manifest)) {
  run_manifest
}
```

## Visualizations

```{r}
figure_dir <- "results/figures"
if (dir.exists(figure_dir)) {
  files <- list.files(figure_dir, pattern = "[.]png$", full.names = TRUE)
  knitr::include_graphics(files)
}
```

## Reporting Checklist

- Motivating research question.
- Prior evidence or theory motivating the selected conditions.
- Manipulated conditions and rationale for levels.
- Data-generating model and population values.
- Fitted model and software details.
- Performance metrics and interpretation standards.
- Tables or figures for the most relevant patterns.
- Conclusions tied back to the research question.
